\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.43in]{geometry}
\usepackage{cmap}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}

\definecolor{accent}{HTML}{1F4E79}
\definecolor{textgray}{HTML}{333333}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\linespread{0.96}
\raggedright
\color{textgray}

\newcommand{\sectiontitle}[1]{%
  \vspace{6pt}
  {\large\bfseries\color{accent}#1}
  \vspace{2pt}
  \hrule height 0.5pt
  \vspace{4pt}
}

\newcommand{\roleentry}[4]{%
  \textbf{#1} \hfill {\small #2}\\
  \textit{#3} \hfill {\small \textit{#4}}
}

\newcommand{\projectentry}[3]{%
  \textbf{#1} \hfill {\small #2}\\
  {\small #3}
}

\setlist[itemize]{leftmargin=*, topsep=2pt, itemsep=1pt, parsep=0pt, partopsep=0pt}

\begin{document}

\begin{center}
  {\LARGE \textbf{Karamveer Singh Sidhu}}\\[-1pt]
  {\normalsize Deep Learning Researcher \textbar{} Full-Stack Software Engineer}\\[2pt]
  \href{mailto:karamveersidhu14@gmail.com}{karamveersidhu14@gmail.com}
  \textbar{} Prince George, BC, Canada
  \textbar{} \href{https://karamveersidhu.com}{karamveersidhu.com}
  \textbar{} \href{https://www.linkedin.com/in/karamveersidhu/}{LinkedIn}
  \textbar{} \href{https://github.com/KaramveerSidhu}{GitHub}
\end{center}

\sectiontitle{Skills}
\textbf{Languages:} TypeScript, JavaScript, Python, C++, Rust, SQL \\
\textbf{Frontend/Backend:} React.js, Next.js, Node.js, NestJS, REST APIs, BullMQ, OAuth, Web3, Design Systems \\
\textbf{ML/Data/Infra:} PyTorch, Flower, Federated Learning, R, Jupyter, PostgreSQL, MongoDB, Redis, Docker, AWS

\sectiontitle{Experience}
\roleentry{Tokenbooks}{June 2025 -- Present}{Software Engineer}{Vancouver, BC}
\begin{itemize}
  \item Build full-stack Web3 finance features across wallet/exchange sync, accounting workflows, reporting, and payments.
  \item Shipped payment request intake, approval routing, counterparty/payment details, and crypto-to-fiat payout flows.
  \item Improved multi-wallet, multi-chain ingestion reliability through async job orchestration, status tracking, structured error handling, Coinbase OAuth reconnect flows, and Excel/XLSX exports.
\end{itemize}

\roleentry{University of Northern British Columbia}{Sept. 2024 -- June 2025}{Graduate Teaching Assistant}{Prince George, BC}
\begin{itemize}
  \item Designed and delivered labs for 110+ students covering statistics and visualization with R and R Commander.
  \item Developed Jupyter/Python labs, taught statistical modeling concepts, provided student support, and assisted with grading and exam invigilation.
\end{itemize}

\roleentry{CloudSEK}{July 2022 -- Aug. 2024}{Software Development Engineer}{Bangalore, India}
\begin{itemize}
  \item Built data visualization components, dashboards, and user-facing pages for XVigil and SVigil; contributed to in-house design system components.
  \item Implemented chunked APK uploads, reducing upload time by 40--50\% while bypassing file size limits.
  \item Developed Exposure Search with other engineers, contributing to 100k+ searches and 3000+ leads; independently shipped a new product frontend within two weeks, supporting a \$100k deal.
\end{itemize}

\sectiontitle{Research \& Projects}
\projectentry{MSc Thesis Research: Causal FL-IDS Defense}{\href{https://github.com/KaramveerSidhu/causal-fl-ids-defense}{GitHub}}{Federated learning robustness for intrusion detection systems}
\begin{itemize}
  \item Designed a causal-defense CNN with a learnable sparse 64x64 causal matrix, aggregated across clients with FedAvg.
  \item Built a reproducible UM-NIDS pipeline and evaluated a 4-client non-IID PyTorch/Flower setup under FGSM and PGD attacks.
  \item Improved PGD robustness from 41.0\% to 89.85\% at epsilon = 0.20 with under 1\% clean-accuracy loss, without adversarial training.
\end{itemize}

\sectiontitle{Education}
\textbf{University of Northern British Columbia} \hfill {\small Sept. 2024 -- June 2026}\\
MSc, Computer Science \hfill {\small GPA: 4.08}\\[2pt]
\textbf{Baba Banda Singh Bahadur Engineering College} \hfill {\small 2018 -- 2022}\\
BTech, Computer Science \hfill {\small CGPA: 8.86}

\sectiontitle{Publications}
\begin{itemize}
  \item \textbf{\href{https://arxiv.org/abs/2601.10004}{SoK: Privacy-aware LLM in Healthcare: Threat Model, Privacy Techniques, Challenges and Recommendations}}. arXiv preprint, 2026.
  \item \textbf{\href{https://doi.org/10.36953/ECJ.2021.SE.2202}{Data science and analytics in agricultural development}}. Environment Conservation Journal, 2021.
  \item \textbf{\href{https://doi.org/10.36953/ECJ.2021.SE.2206}{Advancements in farming and related activities with the help of artificial intelligence: a review}}. Environment Conservation Journal, 2021.
\end{itemize}

\end{document}
